\chapter{Conclusion}
\label{chp:conclusion}



\section{Summary}
%WHAT you are going to present in this chapter/section
%WHY you are presenting it, and
%HOW you are going to present it
A feedback control system was designed, implemented and verified in simulation to swing and balance a robotic gymanst. The feedback control system met all requirements and was able to swing the robotic gymnast from the hanging position and balance in the inverted position.\\
 
The mechanical and electronic hardware were designed to create a robotic gymnast system on which these feedback control systems can be tested. The designed electronic hardware was able to condition the signals for a microcontroller to interpret and supply the feedback control system with the correct signals. The electronic designed provided good resolution of the required state variables and capable of communicating with all peripherals. The mechanical hardware successfully interfaced with the electronic hardware and the provides the means to practically test the feedback control laws.\\

Furthermore the characteristic of the robotic gymnast system was identified and used in simulation. The simulation was shown as a good representation of the designed robotic system to allow further developments on the simulated model. The simulated model fits the experimental responses well and contain the characteristics determine during the system identification.\\

Software was written to acquire the data during experiments and communicate with the electronic hardware. The software allows for various modes of communication such as debugging of subcircuits and streaming of data.\\

\section{Recommendation}
%WHAT you are going to present in this chapter/section
%WHY you are presenting it, and
%HOW you are going to present it
A short description of the improvements that can be made with regards to \textit{The Feedback Control Of A Robotic Gymnast} is provided in this section, in an attempt to improve the quality of future research.\\

Choosing a more advanced microcontroller that is able to use a baudrate greater than 115200 would improve response time and provide better control of the system.\\

Implementing a digital low pass filter to remove the noise on the sampled signal. Especially on the signals that are required to be numerically differentiated.\\

The script executing on the external computer can be written in a language such as C or C++ to increase the execution time of the script.\\


\newpage

	